Sequence complexity

### 2011-07-03 article.tex
Corrected a also

The \textit{where} field doesn't have any meaning when applied to
a digit, and this is already a structural problem.
This same field also doesn't have any meaning either when applied to an increment-operator: it cannot apply to its \textit{argument} because the contained increment-operator takes care of that,
and hence can only apply on its \textit{times}.

>>>>

The \textit{where} field doesn't have any meaning when applied to
a digit, and this is already a structural problem.
This same field doesn't have any meaning either when applied to an increment-operator: it cannot apply to its \textit{argument} because the contained increment-operator takes care of that,
and hence can only apply on its \textit{times}.
